A Fast Unified Model for Parsing and Sentence Understanding

### 2016-03-18 writing/hard_stack_paper/paper.tex
Mention minibatch SGD

We use the RMSProp optimizer \citep{tieleman2012lecture} with a tuned starting learning rate that decays by a factor of 0.75 every 10k steps. We apply both dropout \citep{srivastava2014dropout} and batch normalization \citep{2015SIoffeCSzegedy} to the output of the word embedding projection layer and to the feature vectors that serve as the inputs and outputs to the MLP that precedes the final entailment classifier.

>>>>

We use minibatch SGD with the RMSProp optimizer \citep{tieleman2012lecture} and a tuned starting learning rate that decays by a factor of 0.75 every 10k steps. We apply both dropout \citep{srivastava2014dropout} and batch normalization \citep{2015SIoffeCSzegedy} to the output of the word embedding projection layer and to the feature vectors that serve as the inputs and outputs to the MLP that precedes the final entailment classifier.
